---
title: "Gruppe 9"
author: "Noah Robyr"
format:
  html:
    code-fold: true
    code-tools: true
editor: visual
---

## Theory

### *Research Question:*

How effectively does the Global Party Survey capture the multidimensional nature of populism at party level?

### *Hypothesis:*

H0:

The Global Party Survey\'s populism measures will form coherent dimensions, effectively distinguishing between varying intensities of populism across parties.

H1:

The Global Party Survey\'s populism measures will not form coherent dimensions, effectively distinguishing between varying intensities of populism across parties.

## Running Code

TODO:

Difference btw regions and political positions;

WATCH OUT FOR V18 and V19 (here 0=\>populism and 10=\>not populist) (maybe try to invert the regression ????)

Look if other var correlate with populism (ie Migration or Nationalism);

Render as pdf;

Learn how to use quarto properly;

Try to name the 2 dimension from the EFA and theorize;

See what multilevel regression would do with these underlying dimensions;

#### Libraries

```{r}
library(haven)
library(dplyr)
library(psych)
library(GGally)
library(ggcorrplot) 
library(FactoMineR) 
library(factoextra)   
library(lavaan)
library(tidyverse)
library(GPArotation)
```

#### Getting The Data and splitting the relevant Variables for populism

```{r}
df<-read_dta("Global_Party_Survey.dta")
populism_vars <- df %>% select(V8_Scale, V9, V18, V19, V20, V21)
```

#### Cronbach's Alpha

```{r}
alpha_result <- psych::alpha(populism_vars)
alpha_result
```

The Alpha value being over 0.6 it makes sense to consider that the inner consistency of the values hold

#### Correlation Matrix

```{r}
cor_matrix <- cor(populism_vars, use = "complete.obs")
ggcorrplot(cor_matrix, lab = TRUE, title = "Correlation Matrix for Populism Indicators")
```

#### Explorative Factor Analysis (EFA)

```{r}

nfac<-VSS(populism_vars,n=8,rotate="none",plot =FALSE)
nfac

paf_fit<-fa(populism_vars, nfactors=2, fm = "pa", rotate="varimax")
summary(paf_fit)
paf_fit
print(paf_fit$loadings, cutoff = 0.1) 
fa.diagram(paf_fit, simple = TRUE, main = "EFA Factor Loadings")
```

#### Principal Component Analysis (PCA)

```{r}
pca_result <- PCA(populism_vars, scale.unit = TRUE)
fviz_eig(pca_result)
fviz_pca_var(pca_result, col.var = "contrib", repel = TRUE) +
  labs(title = "PCA of Populism Indicators")
summary(pca_result)
```
